### 2014-03-01 paper/real.tex
First pass at related work section.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
typofix
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

We refer the interested reader to~\tocite{icfp,haskellsymp} for
additional details on the various implementations of this system.
%
Here, we lastly remark that our work unifies these systems and
presents a proof of NI for such systems with asynchronous
communication primitives.

>>>>

We refer the interested reader to~\cite{lio,stefan:addressing-covert} for
additional details on the various implementations of this system.
%
Here, we lastly remark that our work unifies these systems and
presents a proof of non-interference for such systems with asynchronous
communication primitives.
